### 2020-05-10 ArticleAcortado.tex
Seguimos

\textbf{Isomorphisms} between hypergraphs are defined the same as 
isomorphisms between relational structures. We denote the isomorphism relation
between hypergraphs by $\simeq$. 
Given and hypergraph $H$, an \textbf{automorphism} of $H$
is an isomorphism from $H$ to itself. We will denote by
$\aut(H)$ the number of such automorphisms. \par

Let $H$ be an hypergraph and let $V$ be a set. We define the
set of \textbf{copies of $H$ over $V$}, denoted as $Copies(H,V)$, 
as the set of hypergraphs 
$H^\prime$ such that
$V(H^\prime)\subset V$ and $H\simeq H^\prime$.   \par

In our proofs it will be useful to consider colorings over 
hypergraphs as a way to decorate their 
vertices with extra information. 
Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
is a pair $(H, \chi)$ where $H$ is an hypergraph
and $\chi: V(H)\rightarrow \Sigma$ is a map 
called \textbf{$\Sigma$-coloring} of $H$. \par
\textbf{Isomorphisms} between $\Sigma$-hypergraphs are just isomorphisms between the underlying
hypergraphs that also preserve their colorings. We also denote the isomorphism relation between 
$\Sigma$-hypergraphs by $\simeq$.
Given a $\Sigma$-hypergraph $(H,\chi)$,  an 
\textbf{automorphism} of $(H,\chi)$ is an 
isomorphism from it into itself, as before. We will denote
by $\aut(H,\chi)$ the number of such automorphisms. 
\par

Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
As before, we define the set $Copies\big(
(H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $\mathbb{H}$ be 
an isomorphism class of $\Sigma$-hypergraphs. Then the set
$Copies(\mathbb{H}, V)$ is defined as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ such that 
$V(H^\prime)\subset V$ and
$(H^\prime,\chi^\prime)\in \mathbb{H}$. 
Let $v\in V$ and $s\in \Sigma$. We define the
set $Copies\big(\mathbb{H}, V;\,\, (v,s)\big)$ 
as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)\in Copies(\mathbb{H}, V)$
that satisfy $v\in V(H^\prime)$ as well as
$\chi^\prime(v)=s$. \par

@@

@@

The \textbf{center} of an hypergraph $H$, written as
$Center(H)$,  
is the union of all saturated sub- hypergraphs of $H$. 
%	Given $r\in \N$, the $r$-\textbf{center} of $H$,
%	written as $Center(H;r)$, is the union of all saturated 
%	sub-hypergraphs of $H$ with diameter at most $2r+1$.  
Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$. 
%	and let $r\in \N$
If $H$
is connected then we define the graph
$Center(H,\overline{v})$
%	, resp. $Center(H,\overline{v};\, r)$,
as the minimal connected sub-hypergaph of $H$ that contains
both $Center(H)$
%	, resp. $Center(H;\,r)$,
and the vertices in $\overline{v}$. Otherwise,
if $H$ is a general hypergraph we define $Center(H,\overline{v})$,
%	, resp. $Center(H,\overline{v};\, r)$, 
as the union, for all connected components $H^\prime \subset H$,
of the minimal connected sub-hypergraph of $H^\prime$ that
contains both $Center(H^\prime)$
%	, resp. $Center(H^\prime,\overline{v};\, r)$,
and the vertices in $\overline{v}$
that belong to $V(H^\prime)$.

>>>>

Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
is a pair $(H, \chi)$ where $H$ is an hypergraph
and $\chi: V(H)\rightarrow \Sigma$ is a map 
called \textbf{$\Sigma$-coloring} of $H$. \par

\textbf{Isomorphisms} between hypergraphs are defined the same as 
isomorphisms between relational structures. Isomorphisms between $\Sigma$-hypergraphs are just
isomorphisms between the underlying hypergraphs that also preserve their colorings. 
In both cases we denote the isomorphism relation by $\simeq$. 
Given an hypergraph $H$, resp. a $\Sigma$-hypergraph $(H, \chi)$,
an \textbf{automorphism} of $H$, resp. $(H,\chi)$,
is an isomorphism from $H$, resp $(H,\chi)$ to itself.
We will denote by $\aut(H)$, resp. $\aut(H,\chi)$
 the number of such automorphisms. \par

Let $H$ be an hypergraph and let $V$ be a set. We define the
set of \textbf{copies of $H$ over $V$}, denoted as $Copies(H,V)$, 
as the set of hypergraphs 
$H^\prime$ such that
$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Let 
$\chi$ be a $\Sigma$-coloring of $H$. 
As before, we define the set $Copies\big(
(H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $\mathbb{H}$ be 
an isomorphism class of $\Sigma$-hypergraphs. Then the set
$Copies(\mathbb{H}, V)$ is defined as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ such that 
$V(H^\prime)\subset V$ and
$(H^\prime,\chi^\prime)\in \mathbb{H}$. 
Let $v\in V$ and $s\in \Sigma$. We define the
set $Copies\big(\mathbb{H}, V;\,\, (v,s)\big)$ 
as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)\in Copies(\mathbb{H}, V)$
that satisfy $v\in V(H^\prime)$ as well as
$\chi^\prime(v)=s$. \par

@@

\subsection{Main definitions}

\begin{definition}
Let $H$ be a connected hypergraph. If $ex(H)>0$, then it holds that
$H$ contains a unique maximal saturated sub-hypergraph $H^\prime$. 
Furthermore, $H^\prime$ satisfies $ex(H^\prime)=ex(H)$. If $ex(H)\leq 0$ the
set $H^\prime$ as the empty hypergraph. Given
$\overline{v}\in V(H)^*$ we define $Center(H,\overline{v})$ as the 
minimal connected sub-hypergraph in $H$ that contains both $H^\prime$
and the vertices in $\overline{v}$. 
If $H$ is a general hypergraph, not necessarily connected, 
we define $Center(H,\overline{v})$,
%	, resp. $Center(H,\overline{v};\, r)$, 
as the union, for all connected components $H^\prime \subset H$,
of the minimal connected sub-hypergraph of $H^\prime$ that
contains both $Center(H^\prime)$
%	, resp. $Center(H^\prime,\overline{v};\, r)$,
and the vertices in $\overline{v}$
that belong to $V(H^\prime)$.
\end{definition}

@@
